Extended Data

### 2021-12-03 doc/manuscript/Dow_manuscript_Nature.Rmd
fix spelling error

To rule out the possibility that observed patterns were strongly influenced by summer drought, we examined the relationship between spring tempreatures and summer Standardized Precipitation Evapotranspiration Index[@vicente-serrano_multiscalar_2010].
The latter was obtained from the ForestGEO Climate Data Portal v1.0 (https://forestgeo.github.io/Climate/)[@anderson-teixeira_forestgeo_2020; @begueria_standardized_2014;@vicente-serrano_multiscalar_2010a]. 
Linear models were run with 4-, 6-, and 12-month SPEI values of June, July, and August vs April $T_{max}$ to determine if warm spring temperatures were associated with greater summer drought stress in our data set. 
No significant correlations were found (all p>0.05).

>>>>

To rule out the possibility that observed patterns were strongly influenced by summer drought, we examined the relationship between spring temperatures and summer Standardized Precipitation Evapotranspiration Index[@vicente-serrano_multiscalar_2010].
The latter was obtained from the ForestGEO Climate Data Portal v1.0 (https://forestgeo.github.io/Climate/)[@anderson-teixeira_forestgeo_2020; @begueria_standardized_2014;@vicente-serrano_multiscalar_2010a]. 
Linear models were run with 4-, 6-, and 12-month SPEI values of June, July, and August vs April $T_{max}$ to determine if warm spring temperatures were associated with greater summer drought stress in our data set. 
No significant correlations were found (all p>0.05).
